Git Learning Notes

### 2014-02-18 BackMatter/paper.tex
tms further adjusted

\section{TMS}

Raman spectra arise from the inelastic light scattering of optical phonons. In back scattering geometry, the phonon wavevector
$q = 4\pi\frac{n}{\lambda}$. The refractive index of \ce{WS2} at 532nm is about. Compared to the size of Brillouin zone ($\pi/a = 10^{10}m^{-1}$), resonant Raman could or could not probe phonon at $M$ point.

@@

Raman technique could provide valuable insight into the structures of CNT, i.e., tube diameter by assigning the RBMs (radial breathing modes) and G peaks position.\cite{Bonaccorso2013}

 Raman spectroscopy qualifies as an excellent tool to monitor tensile tests of TMDs, both in 2D and in tubular forms.
For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g. by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature. For TMD MWNT, tensile tests have been reported by various groups. However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones. The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected. In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.

>>>>

\section{TMS}
\cite{Cong2013} A direct gap of $\sim 2eV$ at the corners of BZ is formed in 1L \ce{WS2}, Growth on bottom piece show the multiple domain flakes occurs at initial stage of the growth, starting from \ce{WO3} particles.

In Ref\cite{Zeng2013}, single crystal \ce{WS2} growth using \ce{I2} transport was described in supporting info.
\ce{C24H12K4O8}\footnote{http://www.chemspider.com/Chemical-Structure.24771386.html}

@@

For 2D materials, strain may be induced by elongation of an appropriate substrate, e.g. by uniform mechanical strain, or by using a material with high thermal expansion coefficient and varying the temperature. For TMD MWNT, tensile tests have been reported by various groups. However, to date, it is not perfectly clear whether inner and outer walls are stretched simultaneously, or rather the outer walls slide on the inner ones. The latter hypothesis would result in a broadening of the Raman signals, while the first one would leave the signal widths rather unaffected. In any case, there would be a shift of the Raman signals that can serve as precise scale for determining the strain.
